\section{System Qualities}{
  \label{sec:quality_attributes}
  \subsection{Performance}
  Users should be able to rapidly receive feedback representing the current state of the project.
  This includes a preview of the document they wish to create.
  \begin{itemize}
    \pbodyitem{Tactics}{
      \begin{itemize}
        \pbodyitem{Cacheing}{
          Throughout the image creation pipeline, certain modules may not necessarily produce different output, given a user's input.
          Recomputing these results is wasteful, and avoided by implementing a caching layer available to other modules in the system.
          This method involves trading future computational load for memory space.
        }
        \pbodyitem{Profiling}{
          Architects of the system utilize system profiling on typified workloads to determine performance bottlenecks.
          These bottlenecks are then examined and the system is revised to eliminate them.
        }
      \end{itemize}
    }
    \pbodyitem{Scenarios}{
      \begin{itemize}
        \pbodyitem{Region Drawing}{
          When a user draws a region mask on the preview pane, the system should display a preview of the mask within one-tenth of a second.

          \lidiagram{diagrams/scenarios/region_drawing}
          {GlyphMosaic gives near-instantaneous feedback for region specification.}
          {fig:sc-reg-draw}
        }
        \pbodyitem{Mosaic Preview ``Cold'' Response}{
          When a user opens the preview pane, it should display a preview of the mosaic within one second.
        }
        \pbodyitem{Mosaic Preview ``Warm'' Response}{
          When a user changes a parameter in the document while the preview pane is already open and viewing a result of that change, the user should see the result of that change within one-quarter of one second.
        }
        \pbodyitem{Mosaic Full Render Response}{
          When the user triggers a full render of the document, the system should write the result to the host filesystem within 20 seconds.
        }
      \end{itemize}
    }
  \end{itemize}
 }