\section{Requirements}
Requirements for GlyphMosaic aim to create a responsive and productive environment for its users.
The GlyphMosaic System provides a specialized method to build unique graphic mosaic designs.


\subsection{Functionality}
GlyphMosaic’s main built-in functionality is focused entirely on the workflow of creating mosaics.
In the most common workflow,
\begin{enumerate}
      \item a user will load the source image and text into the program...
      \item ...adjust various document parameters...
      \item ...render a high-resolution version of the output mosaic...
      \item ...save that file for use outside the application.
\end{enumerate}


\subsection{Differentiation}
Existing systems perform a similar, but limited subset, of the functionality of the system.
One system can specify various line patterns, such as spirals.
Many other examples exist that focus solely on LTR horizontal mosaics.

GlyphMosaic's pathing is \gls{bitmap}-based, using \glspl{glyph_path_kernel} instead of mathematical equations.
Mosaic creators can specify the glyph line pattern by specifying a line kernel.
Areas of the source image which require different path kernels are differentiated by region.

The system uses the kernel dilation iteration paths to stamp glyphs from the \gls{src_txt} along the \gls{glyph_path}, scaling according to the \gls{density} from the \gls{src_img} to arrive at the \gls{out_image}.

Because glyph paths are built from bitmaps instead of mathematical expressions, designers have more options to specify complexity.
This path complexity enables more distinctive patterns, such as following a fold in a piece of fabric, the curves on a bowl, or the weave of a fabric, among others.

\subsection{Use Cases}
\label{sec:use_cases}

\lidiagram{diagrams/use_case_diagram}
{User-system interactions are constrained by the workflow.}
{fig:use_case}

\begin{itemize}
      \lbodyitem{System Installation}{
      \item Users must be able to download, install, and run the system on their own devices.
            }
            \lbodyitem{Content Creation}{
      \item Users must be able to create and modify GM documents.
            }
\end{itemize}

This workflow is further detailed in \prettyref{sec:user_workflow_model}.